\boldmath Flavour Symmetry Embedded - GLoBES

### 2020-04-28 doc/FAS-GLoBES.tex
Update FAS-GLoBES.tex

We now take the littlest seesaw model in the tri-direct approach as an example. In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
where  stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
\begin{equation}
\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
 1 &~ \omega  &~ \omega ^2 \\
 \omega  &~ \omega ^2 &~ 1 \\
 \omega ^2 &~ 1 &~ \omega  \\
\end{pmatrix}+e^{i\eta}m_{s}
\begin{pmatrix}
 1 &~  x &~  x \\
 x &~ x^2 &~ x^2 \\
 x &~ x^2 &~ x^2 \\
\end{pmatrix}\,,
\end{equation}
where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data. We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FASE-GLoBES}. We will introduce the way to do it in Sec.~\ref{sec:prior}.

@@

For different methods to include the model, we use different \texttt{c++} file. Adopting the mass matrix Eq.~\ref{eq:mnu}, we assign this model in \textbf{model-input\_diag.c}. In function \texttt{MtoS}, we give
the mass matrix Eq.~\ref{eq:mnu} in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.\vspace{0.5cm}

@@

Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$. The expression of \texttt{Mass\_Matrix[]} is given by the user. For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.

We can also assign the relation between oscillation and model parameters Table~\ref{tab:TD_parameters} in \textbf{model-input.c}. The relations are given in \texttt{MtoS} as well.\vspace{0.5cm}

@@

\section{Examples}
\subsection{Constraint of model parameters}
%\subsection{Projection on the PMNS parameters}
\begin{figure}[!h]%
\centering
\includegraphics[width=2in]{figs/x.pdf}
\includegraphics[width=2in]{figs/eta.pdf}\\
\includegraphics[width=2in]{figs/r.pdf}
\includegraphics[width=2in]{figs/ma.pdf}
\caption{The $\Delta\chi^2$ value against each model parameters for MOMENT. True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$. The range shown here is according to the $3\sigma$ uncertainty with NuFit4.0 results:  $-5.475<x<-3.37$ (red band),~$0.455<\eta/\pi<1.545$ (dark grey band), ~$0.204<r<0.606$ (blue band),~$3.343<m_a/\text{meV}<4.597$ (yellow band).}%
\label{fig:model_1D}
\end{figure}

>>>>

For different methods to include the model, we use different \texttt{c++} file. Adopting the mass matrix expressed by model parameters, we assign this model in \textbf{model-input\_diag.c}. In function \texttt{MtoS}, we give
the mass matrix in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.
%
Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$. The expression of \texttt{Mass\_Matrix[]} is given by the user. For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.  We can also assign the relation between oscillation and model parameters in \textbf{model-input.c}. The relations are given in \texttt{MtoS} as well.

\section{Examples}
\subsection{Setup for a model}
We now take the littlest seesaw model in the tri-direct approach as an example. In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
where  stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
\begin{equation}
\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
 1 &~ \omega  &~ \omega ^2 \\
 \omega  &~ \omega ^2 &~ 1 \\
 \omega ^2 &~ 1 &~ \omega  \\
\end{pmatrix}+e^{i\eta}m_{s}
\begin{pmatrix}
 1 &~  x &~  x \\
 x &~ x^2 &~ x^2 \\
 x &~ x^2 &~ x^2 \\
\end{pmatrix}\,,
\end{equation}
where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data. We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FASE-GLoBES}. We will introduce the way to do it in Sec.~\ref{sec:prior}.

@@

@@

@@

\subsection{Constraint of model parameters}
%\subsection{Projection on the PMNS parameters}
\begin{figure}[!h]%
\centering
\includegraphics[width=2in]{figs/x.pdf}
\includegraphics[width=2in]{figs/eta.pdf}\\
\includegraphics[width=2in]{figs/r.pdf}
\includegraphics[width=2in]{figs/ma.pdf}
\caption{The $\Delta\chi^2$ value against each model parameters for MOMENT. True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$. The range shown here is according to the $3\sigma$ uncertainty with NuFit4.0 results:  $-5.475<x<-3.37$ (red band),~$0.455<\eta/\pi<1.545$ (dark grey band), ~$0.204<r<0.606$ (blue band),~$3.343<m_a/\text{meV}<4.597$ (yellow band).}%
\label{fig:model_1D}
\end{figure}
